---
title: "Exercise Sheet 3"
author: "Lea Kunze"
date: "2025-05-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **d) Name 2 strengths and 2 weaknesses of Git.**

**Strengths:**

1.  **Version Control:** Git allows you to track changes over time, revert to previous versions, and work on different branches without affecting the main code.

2.  **Collaboration:** Multiple people can work on the same project simultaneously, and Git provides powerful tools to merge changes and resolve conflicts.

**Weaknesses:**

1.  **Steep Learning Curve:** Beginners can find Git difficult to learn, especially when dealing with merge conflicts or using advanced commands.

2.  **Complex History:** For larger projects, the commit history can become messy and hard to understand if not managed properly.

##  Exercise 3: Pixar Films 

### a) 

```{r}
library(tidyverse)

pixar <- read_csv("pixar_films.csv") %>%
  filter(!is.na(film))

unique(pixar$film_rating)

pixar <- pixar %>%
  mutate(film_rating = factor(film_rating))
```

The variable `film_rating` contains values based on the Motion Picture Association (MPA) film rating system. It describes how films are rated for content suitability.

By inspecting the dataset, we can see that the possible values for `film_rating` are labels such as `"G"`, `"PG"`, `"PG-13"`, or `"NR"`. These represent different rating categories from the MPA system, but the dataset itself does not define the exact meanings. It only tells us that the ratings follow the MPA standard.

Creating a **factor variable** for `film_rating` is appropriate because the ratings represent a fixed set of **categorical values**. Factors are useful for modeling and plotting categorical data and help ensure that R treats the values as discrete levels instead of free-form text.

### b)

```{r}
library(dplyr)
library(stringr)
# Manually film titles
movies <- data.frame(
  reihe = c(
    "A Bug's Life", "Brave", "Cars", "Cars 2", "Cars 3", "Coco", "Finding Dory", "Finding Nemo", "Incredibles 2", "Inside Out", "Lightyear", "Luca", "Monsters University", "Monsters, Inc.", "Onward", "Ratatouille", "The Good Dinosaur", "The Incredibles", "Toy Story", "Toy Story 2", "Toy Story 3", "Toy Story 4", "Turning Red", "Up", "WALL-E" 
    ),
  stringsAsFactors = FALSE
)

movies$series <- c(
  "Standalone", "Standalone", "Cars", "Cars", "Cars", "Standalone", "Finding Nemo", "Finding Nemo",
  "The Incredibles", "Standalone", "Standalone", "Standalone", "Monsters, Inc.", "Monsters, Inc.",
  "Standalone", "Standalone", "Standalone", "The Incredibles", "Toy Story", "Toy Story", 
  "Toy Story", "Toy Story", "Standalone", "Standalone", "Standalone"
)

# Groub by series and summarize
library(dplyr)

series_summary <- movies %>%
  group_by(series) %>%
  summarise(
    titles = paste(reihe, collapse = ", "),
    count = n()
  ) %>%
  ungroup()

print(series_summary)

```

### c)

```{r}
# load data
public_response <- read.csv("public_response.csv")

levels_order <- sort(unique(public_response$cinema_score))
public_response$cinema_score <- factor(public_response$cinema_score, levels = levels_order, ordered = TRUE)
# merge 
combined_data <- merge(public_response, pixar, by = "film")
```
